\chapter{\label{chap:challenges}Challenges}

During the development of the projects some challanges arose. Deployment with
TerraForm can be tricky since there as a 4MB limit for files which makes
especially the deployment of Rust functions difficult because those are usually
compiled as a single application that in many instance will shoot over the 4MB
limit. The reason are the included libraries. An example would be a library for
web requests. Even with TypeScript the mentioned limits can be seen although it
is in this case only text, that will be uploaded. The JavaScript AWS API is
quite large and cause problems during the upload to IBM therefore.

While the deployment of the functions was only done on IBM, an AWS account was
still required since the forecast functions relies on AWS forecast, which is
obvously only available on AWS. For students AWS offers the AWS student
program, which lets students use their service for 3 hours per session. This
can be a problem since unfortunatally those 3 hours are bound to a web page
session.  The said web-page is unreliable to say the least and tends to crash
quite frequently, which is especially troublesome during the run of the
forecast function, which takes about 50 minutes to complete.

Serverless computing as a whole is a great concept, which we would use outside
of the course as well. However for the task at hand it is not the best solution,
because running one serverless function for 50 minutes would be expensive and
kind of negates the benefits of serverless computing. A VM for the forecast function
in particular would be a better solution.



\textcolor{magenta}{Tentative challenges length: between a half and one page.}

\vspace{20 pt}

Keep only those sections that are relevant for you.

\vspace{20 pt}

Explain in detail the challenges you faced during functions development, FC development, deployment, and execution.


%
%
%
\section{FaaS system challenges}

Which challenges have you faced with:

\begin{itemize}
    \item hdd limitations
    \item the size of data inputs or outputs
    \item code size
    \item deployment tools limitations
    \item other limitations
\end{itemize}



%
%
%
\section{FaaS development challenges}

What frustrated you the most when using FaaS?
After your experience, would you use FaaS (instead of VMs/Containers) if you weren't forced to as part of a course? Why, why not?



%
%
%
\section{FC challenges}

Did you face any limitations of AFCL which challenged you to develop the FC?
