\chapter{\label{chap:conclusion}Conclusion \& Future Work}

In this project, we built a serverless system to predict the stock prices for
the next day using historical data. Multiple stock ticker symbols are passed as
input and as output, a graph is generated showing the predicted prices. This
simplifies and automates multiple tasks that would have to be done manually for
each stock. During the development and eveloation of the FC it was clear that
serverless computing is not suitable for each function in the FC. The forecast
function was particularly problematic as it's task was longer than the
permitted runtime per function. Overall it can be said, that while the setup as
is can work a better solution would be to run at least the forecast function on
a VM. The development itself was not always straight forward as there were some
issues with APIs regarding keys and usage as well as deployment. The
development was split evenly among the team members, where each member worked
on two Rust and two TypeScript functions and the deployment process was
automated together by both members.

% TODO: State your contributions. Use the numbers from the experimental evaluation to provide evidence of the improvement resulting from your work.



%
%
%
\section{Future Work}

Future work on this project would definitely include finding an alternative
solution to AWS Forecast which does not require such an elaborate setup for
predicting prices.  Due to the complicated API we only became aware of this
issue after we had already implemented the bulk of the forecast function in
both Rust and JavaScript, which is why we did not have time to find another
forecasting solution which works in both languages.



%
%
%
\section{Recommendations for the VU in the Future}

I kindly ask you for a feedback regarding:
\begin{itemize}
    \item The homeworks were fairly straight-forward to solve, however sometimes quite time-consuming.

    \item The project was quite interesting and also fairly straight-forward to implement,
          however using AWS Forecast and two languages took a lot more time than anticipated.

    \item Would you like to focus on multiple FaaS systems from the beginning with multiple cloud services (e.g. IBM Watson, Google AI, …)? \\
          No, the platform is not that important, so a single one is fine.

    \item Is the depth of the selected topics appropriate? \\
          Yes.

    \item Are the selected topics appropriate? \\
          Yes.

    \item What would you like to learn more? \\
          Kubernetes

    \item What would you like to be removed from the course? \\
          Java
\end{itemize}
